### 2018-09-18 Chapters/Chapter3.tex
Correction
commit with cancer

\begin{align}
J_{ij}(t) &= \sum_{mn} \left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
&= \sum_{mn} (-1)^m t_0^2 \left( \frac{J_{m-n}(\alpha_{ji})J_n(\alpha_{ij})}{U+n\omega} +\frac{J_n(\alpha_{ji})J_{(m-n)}(\alpha_{ij})}{U-n\omega} \right)
\end{align}

@@

\begin{equation}
J_{ij} = 2 t_0^2 \alpha_{ij}^2 \left( \frac{1}{U-\omega} - \frac{1}{U} + \frac{1}{U+\omega} \right)
\end{equation}

@@

>>>>

\begin{align}
J_{ij}(t) &= \sum_{mn} 2\left( \frac{t_{ji,(m-n)} t_{ij,n}}{U+n\omega} + \frac{t_{ji,n} t_{ij,(m-n)}}{U-n\omega} \right) e^{im\omega t} \nonumber \\
&= \sum_{mn} 2(-1)^m t_0^2 \left( \frac{J_{m-n}(\alpha_{ji})J_n(\alpha_{ij})}{U+n\omega} +\frac{J_n(\alpha_{ji})J_{(m-n)}(\alpha_{ij})}{U-n\omega} \right)
\end{align}

@@

\begin{equation}
J_{ij} = 4 t_0^2 \left( \frac{\alpha_{ij}^2}{U-\omega} + \frac{1}{U} + \frac{\alpha_{ij}^2}{U+\omega} \right)
\end{equation}

@@

Notice that this substitution also applies if we add a Rashba Spin-Orbit interaction term to \ref{HamEMF}, i.e., if $\hat{H}'(\bs{r}) = \frac{(\bs{p}-e\bs{A})^2}{2m} +U(\bs{r}) + \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A}))$, then

\begin{equation}
  \alpha_R \hat{z}(\hat{\bs{\sigma}} \times (\bs{p}-e\bs{A})) \psi'_{\bs{R}} = \alpha_R(\hat{\sigma_x}(\hat{p}_y-e\bs{A}) - \hat{\sigma_y}(\hat{p}_x-e\bs{A})) e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}} \psi_{\bs{R}}}=  e^{i\frac{e}{\hbar}\int_{\bs{R}}^{\bs{r}}} \alpha_R \hat{z}(\hat{\bs{\sigma}} \times \bs{p} \psi_{\bs{R}} 
\end{equation}
